---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, eval=FALSE}
install.packages(devtools)
library(devtools)
install_bitbucket("greymonroe/TSPmap")
```

```{r}
library(TSPmap)
```


```{r}
LKHexec = "~/TSPexecs/LKH"
Concordepath = "~/TSPexecs/concorde_mac"
```


```{r}
rawdata = readFile(system.file("extdata", "JM20Demo_rawinput.tsv", package = "TSPmap"))
```

```{r}
duplicates = finddups(rawdata, threshold = 99)
str(duplicates)
```

```{r}
rawdata = removedups(rawdata, duplicates)
```

```{r}
rfmat = computeRFmat(rawdata, corrFlag=T)
```

```{r}
rfmatclean = cleanrfmat(rfmat)
rfmatclean = addMarkerNames(rfmatclean, rawdata)
```

```{r}
rfCap = 0.4
cappedrfmat = capRFmat(rfmat, rfCap, capval = 0.5)
```

```{r}
numChromosomes = 5
```

```{r}
rawclusters = autoClusterMST(rawdata, cappedrfmat, numChromosomes, LKHexec, internalRfThreshold=0.4)
```

```{r}
mergedclusters = autoMergeClusters(rawclusters, cappedrfmat, LKHexec, numChromosomes, rfCap, rawdata=rawdata)
```

```{r}
finalMap = list()
for(i in 1:length(mergedclusters))
{
  finalMap[[i]] = createMap(rawdata, cappedrfmat, mergedclusters[i], Concordepath)
}
```

```{r}
finalMap = finalMap[!sapply(finalMap, is.null)]
```

```{r}
distancedf<-TSPmap2distancedf(finalMap)
```

```{r}
markers<-reorderMarkers(rawdata = rawdata, distancedf = distancedf)
```

```{r, eval=F }
write.table(markers, file = "/Users/greymonroe/Desktop/orderedMarkers.csv", sep=",", row.names = F)
Rqtlmap<-qtl::read.cross(file = "/Users/greymonroe/Desktop/orderedMarkers.csv", format = "csv", genotypes = c("a","b" ,"-"))
```

```{r}
markertable<-distancedf2table(distancedf = distancedf)
head(markertable)
Rqtlmap<-#qtl::table2map(markertable)
```




Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
