---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Installation

```{r, eval=FALSE}
install.packages(devtools)
library(devtools)
install_bitbucket("greymonroe/TSPmap")
```

## Load package
```{r}
library(TSPmap)
```

# TSP solvers

TSPmap requires two existing tools to find the optimal solution:
LKH, http://www.akira.ruc.dk/~keld/research/LKH/
Concorde, http://www.math.uwaterloo.ca/tsp/concorde.html

Download the exceutable files approprirate for your system. The path to the each executable file must be specified in your code to call for functions within TSPmap:

```{r}
LKHexec = "~/TSPexecs/LKH"
Concordepath = "~/TSPexecs/concorde_mac"
```

# Create linkage map from marker data

## Read in raw data. The code provided below loads a dataset that comes wtih the TSPmap package.
```{r}
rawdata = readFile(system.file("extdata", "JM20Demo_rawinput.tsv", package = "TSPmap"))
```

## Identify and remove duplicate markers.

```{r}
duplicates = finddups(rawdata, threshold = 99)
rawdata = removedups(rawdata, duplicates)
```

## Calculate recombination frequency between markers.
```{r}
rfmat = computeRFmat(rawdata, corrFlag=T)
```

## Create 'clean' recombination frequency matrix for more easy visualization.
```{r}
rfmatclean = cleanrfmat(rfmat)
rfmatclean = addMarkerNames(rfmatclean, rawdata)
```

## Adjust recombination frequency values
Because it is detrimental to the performance of the TSP solver to allow these values to remain in the analysis, the user may input a cutoff threshold (default set to 0.4) above which all rf values are inflated to 0.5, preventing the solver from spending computation time optimizing these non-informative values.  However, setting the threshold too low can begin to affect the clustering and the final ordering of markers within the linkage group. This is especially true for noisy data sets, since meaningful rf values may be relatively high when there is a lot of noise in the data. 
```{r}
rfCap = 0.4
cappedrfmat = capRFmat(rfmat, rfCap, capval = 0.5)
```

```{r}
numChromosomes = 5
```

```{r}
rawclusters = autoClusterMST(rawdata, cappedrfmat, numChromosomes, LKHexec, internalRfThreshold=0.4)
```

```{r}
mergedclusters = autoMergeClusters(rawclusters, cappedrfmat, LKHexec, numChromosomes, rfCap, rawdata=rawdata)
```

```{r}
finalMap = list()
for(i in 1:length(mergedclusters))
{
  finalMap[[i]] = createMap(rawdata, cappedrfmat, mergedclusters[i], Concordepath)
}
```

```{r}
finalMap = finalMap[!sapply(finalMap, is.null)]
```

```{r}
distancedf<-TSPmap2distancedf(finalMap)
```

```{r}
markers<-reorderMarkers(rawdata = rawdata, distancedf = distancedf)
```

```{r, eval=F }
write.table(markers, file = "/Users/greymonroe/Desktop/orderedMarkers.csv", sep=",", row.names = F)
Rqtlmap<-qtl::read.cross(file = "/Users/greymonroe/Desktop/orderedMarkers.csv", format = "csv", genotypes = c("a","b" ,"-"))
```

```{r}
markertable<-distancedf2table(distancedf = distancedf)
head(markertable)
#Rqtlmap<-qtl::table2map(markertable)
```




Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
